### 2019-11-07 Action letter.Rmd
Sent to Renske

We thank you and the Reviewers for your thorough comments, for the helpful summary you've provided. We hope that you will find that our responses adequately address the issues raised, and that the quality of the work has been improved.

<!--The manuscript (including title page, abstract, and references) comprises 35 pages, or 8666 words. Four supplementary tables are included, whose size prohibits them from being included in the manuscript: A full correlation table (total sample and paneled by adolescent sex); the full matrix of parameter estimates; detailed scale descriptives and intercorrelations, and a full matrix of parameter estimates for an alternative analysis suggested by a Reviewer. 
Should the manuscript be submitted, we are prepared to make all syntax and results of the analyses conducted available on a public code repository referenced in the paper, to safeguard reproducibility. 
Treatment of participants was in accordance with the APA ethical principles. On behalf of the authors, I declare that I have no conflicts of interest concerning this article. I will serve as the corresponding author for this manuscript.-->

@@

1. We have unmasked all sections in the revised manuscript that describe the sample, so the Reviewers can assess its quality and generalizability.
2. Bayesian estimation handles missing data intrinsically, in a similar way to FIML. We have explained this in the revised manuscript and in this letter.
3. Attrition is minor, and is covered in Supplementary Table S1. In the revised manuscript, we now explicitly refer to all information covered in S1 (scale descriptive statistics, number of items, number of complete cases, and reliability).

@@

\RC{This manuscript addresses an important research area: understanding the role of mothers and fathers in the emotional adjustment of children.  Strengths of this paper include (a) the inclusion of quantitative and qualitative measures of parenting from both parents, (b) a within- and between-person design, and (c) a longitudinal study with repeated measures of children and parenting. Below, I describe my suggestions to improve the manuscript as currently written.}

@@

\RC{The first paragraph of the introduction introduces many different ideas and comes across as disjointed. Revision should make it clear to readers that the focus is on emotional adjustment among children (as well as the specific developmental age of focus), describe a more complex, well-cited definition of emotional adjustment (the current citation and definition does not seem accurate), introduce the idea that mothers and fathers may plan a unique role in the development of emotional adjustment, before focusing in on the role of fathers. Finally, it would help the reader to provide the research goals in the first 1-2 pages of the introduction to get a sense where the paper is headed.}

@@

\RC{The authors make the argument that developmental psychology has emphasized qualitative parenting behaviors whereas sociology and gender studies have focused on involvement quantity. The authors need to defend this point with more citations and nuance, but more broadly, perhaps the focus should move away from disciplinary differences in order to explain and justify why including both types of measures is important. It's seems this later idea is what the authors are intending to put forward to the reader but it gets lost a bit when describing disciplinary differences that do not seem precise.}

@@

\RC{The remaining introduction is thorough in its review, but needs more synthesis and direction for the reader. Providing the research goals toward the beginning of the introduction and then carefully walking the reader through the relevant existing literature may help to do this.}

@@

\RC{While the possibility of sex differences is brought up in the introduction, it is not brought forth in the research questions so it is unclear if the authors are going to investigate it, despite their justification for doing so.}

@@

\RC{Finally, hypotheses based upon the existing literature and theory would be useful in the introduction.}

@@

\RC{The annual income of the parents seems quite low, and the decision to focus only on non-minority families raises questions, however perhaps this is due to my lack of knowledge of the context in which this study is placed. It would be helpful to specify the geographic area of the study to provide some context. Similarly, more information on the sample is needed to understand how these results may or may not generalize to broader populations.}

@@

@@

\RC{More information on all of the scales should be provided. Specifically, the number of items in each scale, reliability statistics...}

@@

\RC{...any information on external validity...}

@@

\RC{...and the reporter. It was unclear to me that the measure of emotional adjustment was teacher reported until the limitations section.}

@@

\RC{There is also more information needed on study recruitment, who were the participants, when each round of data collection took place, how the assessments were completed, ect.}

@@

\RC{Relatedly, how did the authors handle missing data across the study waves?}

@@

\RC{Please include effect sizes when describing the results.}

@@

\RC{What are the values in the tables? Please include this in a table note and describe in the text.}

@@

\RC{How were sex differences tested in the analytic models?}

@@

\RC{Showing the results in the form of figures and tables would be very helpful for readers.}

@@

\RC{When the authors describe effects as being larger for fathers in comparison to mothers, did they test this statistically?}

@@

\RC{Discussion: I am unsure of the context of this study, but there seem to be issues in terms of the representativeness of the sample and therefore these issues should be references in the limitations section.}

\RC{Minor points:
* In the first sentence of the abstract, I believe it should be "The question of whether…" rather than "The question whether…"}

@@

\RC{* Extra spaces between paragraphs should be removed}

@@

\RC{* Miss spelling on page 12: agerage}

@@

We completely agree with the Reviewer that warmth and security, provided by either parent, are positively related to emotional adjustment development. We discuss this in REFER TO PARAGRAPH. It appears that the Reviewer interpreted the word *uniquely* to mean that *only* fathers contribute to emotional adjustment. We intended to say that fathers contribute in a *different* way from mothers.   
We merely intended to summarize fatherhood theory regarding the distinction between the attachment vs activation relationship: A widely endorsed theory that posits that demandingness is a more important socialization mechanism for fathers than for mothers, and that warmth is a more important socialization mechanism for mothers than for fathers.

@@

@@

@@

@@

We appreciate the Reviewer's suggestion, and agree that there are probably good grounds to question the linearity of *all* processes within the family system. However, it is not within the scope of the present paper to make that point. In principle, we would be happy to conduct the exploratory analysis proposed by the Reviewer, but we are stopped by the limitations of contemporary statistical software. Including a quadratic term for this non-linear effect requires estimating a latent variable interaction of quantitative involvement with itself. Such latent variable interactions cannot currently be estimated within the Bayesian framework; they require Monte Carlo integration. Thus, we must choose: We can either test our theoretical model, which requires Bayesian estimation using Gibbs sampling, or we analyze this proposed non-linear effect, but within a much simpler model that can be estimated using numerical integration. Of course, we would prefer to analyze our theoretical model.

@@

We agree with the Reviewer that mean differences in emotional adjustment based on low vs high involvement are important. That is why we do investiage these effects, and they are reported in the section titled **Effects of quantitative involvement on parenting _and adjustment_**. That is why we suggested those explanations in the Discussion. Here are the relevant fragments from the Results section:

>>>>

We thank you and the Reviewers for your thorough comments, and for the helpful summary you've provided. We hope that you will find that our responses adequately address the issues raised, and that the quality of the work has been improved.

<!--The revised manuscript (including title page, abstract, and references) comprises 35 pages, or 8666 words. Four supplementary tables are included, whose size prohibits them from being included in the manuscript: A full correlation table (total sample and paneled by adolescent sex); the full matrix of parameter estimates; detailed scale descriptives and intercorrelations, and a full matrix of parameter estimates for an alternative analysis suggested by a Reviewer. 
Should the manuscript be accepted, we are prepared to make all syntax and results of the analyses conducted available on a public code repository referenced in the paper, to safeguard reproducibility. 
Treatment of participants was in accordance with the APA ethical principles. On behalf of the authors, I declare that I have no conflicts of interest concerning this article. I will serve as the corresponding author for this manuscript.-->

@@

1. We have unmasked all sections in the revised manuscript that describe the sample, so the Reviewers can assess its quality and generalizability. We also address generalizability in the *Limitations* section.

The *Participants* section now reads:

> We employed data from the `r masked("K-cohort")` of the `r masked("Longitudinal Study of Australian Children (LSAC)")`, waves `r masked("2-5")`, which were collected by means of biannual home visits, and self-report mail questionnaires, from 2006-2012. Each wave was reviewed and approved by the
`r masked("Australian Institute of Family Studies Ethics Committee")`, which is a Human Research
Ethics Committee registered with the `r masked("National Health and Medical Research Council")`. Documentation of the ethics approval is available online at `r masked("https://growingupinaustralia.gov.au/sites/default/files/certification_of_ethics_approval_for_lsac.pdf")`. `r masked("LSAC")` employed a clustered sampling design to obtain a representative sample of the `r masked("Australian")` population. Complete details regarding the study design, sample, and procedure are available online at `r masked("http://data.growingupinaustralia.gov.au/")`.

The *Limitations* section now reads:

> A final potential limitation pertains to the generalizability of the findings. Our target sample consisted of native `r masked("Australian")`, non-minority, intact, biological families. It is possible, but beyond the scope of this study, that the findings might have limited generalizability for Australian minorities, or for families in other industrialized nations.

2. Bayesian estimation handles missing data intrinsically, in a similar way to FIML. We have explained this in the revised manuscript (below) and in this letter (see our response to Reviewer 1, comment 1.10).

> Bayes is a full-information estimator, which means that all available information is used without imputing missing values, and consistent estimation is guaranteed under the assumption that data are missing at random. The missing data handling is likelihood based and guarantees consistent estimation as long as the missing data is missing at random (MAR).

3. Attrition is minor, and is covered in Supplementary Table S1. In the revised manuscript, we now explicitly refer to all information covered in S1 (scale descriptive statistics, number of items, number of complete cases, and reliability).

@@

\RC{1.1 This manuscript addresses an important research area: understanding the role of mothers and fathers in the emotional adjustment of children.  Strengths of this paper include (a) the inclusion of quantitative and qualitative measures of parenting from both parents, (b) a within- and between-person design, and (c) a longitudinal study with repeated measures of children and parenting. Below, I describe my suggestions to improve the manuscript as currently written.}

@@

\RC{1.2a The first paragraph of the introduction introduces many different ideas and comes across as disjointed. Revision should make it clear to readers that the focus is on emotional adjustment among children (as well as the specific developmental age of focus)...}

\RC{1.2b ...describe a more complex, well-cited definition of emotional adjustment (the current citation and definition does not seem accurate)...}

We operationalized emotional adjustment in terms of the emotional adjustment subscale of the SDQ. Consequently, we cite the scale validation paper of the SDQ here. It is not evident to us what other reference would be more appropriate than the one we used to operationalize this construct, but if the Reviewer feels that a particular citation should be included, we are happy to do so.

\RC{1.2c ...introduce the idea that mothers and fathers may plan a unique role in the development of emotional adjustment, before focusing in on the role of fathers. Finally, it would help the reader to provide the research goals in the first 1-2 pages of the introduction to get a sense where the paper is headed.}

@@

\RC{1.3 The authors make the argument that developmental psychology has emphasized qualitative parenting behaviors whereas sociology and gender studies have focused on involvement quantity. The authors need to defend this point with more citations and nuance, but more broadly, perhaps the focus should move away from disciplinary differences in order to explain and justify why including both types of measures is important. It's seems this later idea is what the authors are intending to put forward to the reader but it gets lost a bit when describing disciplinary differences that do not seem precise.}

@@

\RC{1.4 The remaining introduction is thorough in its review, but needs more synthesis and direction for the reader. Providing the research goals toward the beginning of the introduction and then carefully walking the reader through the relevant existing literature may help to do this.}

@@

\RC{1.5 While the possibility of sex differences is brought up in the introduction, it is not brought forth in the research questions so it is unclear if the authors are going to investigate it, despite their justification for doing so.}

@@

\RC{1.6 Finally, hypotheses based upon the existing literature and theory would be useful in the introduction.}

@@

\RC{1.7 The annual income of the parents seems quite low, and the decision to focus only on non-minority families raises questions, however perhaps this is due to my lack of knowledge of the context in which this study is placed. It would be helpful to specify the geographic area of the study to provide some context. Similarly, more information on the sample is needed to understand how these results may or may not generalize to broader populations.}

@@

Furthermore, we now address generalizability in the *Limitations* section:

> A final potential limitation pertains to the generalizability of the findings. Our target sample consisted of native `r masked("Australian")`, non-minority, intact, biological families. It is possible, but beyond the scope of this study, that the findings might have limited generalizability for Australian minorities, or for families in other industrialized nations.

@@

\RC{1.8a More information on all of the scales should be provided. Specifically, the number of items in each scale, reliability statistics...}

@@

\RC{1.8b ...any information on external validity...}

@@

\RC{1.8c ...and the reporter. It was unclear to me that the measure of emotional adjustment was teacher reported until the limitations section.}

@@

\RC{1.9 There is also more information needed on study recruitment, who were the participants, when each round of data collection took place, how the assessments were completed, ect.}

@@

\RC{1.10 Relatedly, how did the authors handle missing data across the study waves?}

@@

\RC{1.11 Please include effect sizes when describing the results.}

@@

\RC{1.12 What are the values in the tables? Please include this in a table note and describe in the text.}

@@

\RC{1.13 How were sex differences tested in the analytic models?}

@@

\RC{1.14 Showing the results in the form of figures and tables would be very helpful for readers.}

@@

\RC{1.15 When the authors describe effects as being larger for fathers in comparison to mothers, did they test this statistically?}

@@

\RC{1.16 Discussion: I am unsure of the context of this study, but there seem to be issues in terms of the representativeness of the sample and therefore these issues should be references in the limitations section.}

We have attempted to address this comment by unmasking the *Participants* section (see below), and discussing generalizability in the *Limitations* section (see our response to 1.7).

The *Participants* section now reads:

> We employed data from the `r masked("K-cohort")` of the `r masked("Longitudinal Study of Australian Children (LSAC)")`, waves `r masked("2-5")`, which were collected by means of biannual home visits, and self-report mail questionnaires, from 2006-2012. Each wave was reviewed and approved by the
`r masked("Australian Institute of Family Studies Ethics Committee")`, which is a Human Research
Ethics Committee registered with the `r masked("National Health and Medical Research Council")`. Documentation of the ethics approval is available online at `r masked("https://growingupinaustralia.gov.au/sites/default/files/certification_of_ethics_approval_for_lsac.pdf")`. `r masked("LSAC")` employed a clustered sampling design to obtain a representative sample of the `r masked("Australian")` population. Complete details regarding the study design, sample, and procedure are available online at `r masked("http://data.growingupinaustralia.gov.au/")`.

\RC{1.17 Minor points:
* In the first sentence of the abstract, I believe it should be "The question of whether…" rather than "The question whether…"}

@@

\RC{1.18 * Extra spaces between paragraphs should be removed}

@@

\RC{1.19 * Miss spelling on page 12: agerage}

@@

We completely agree with the Reviewer that warmth and security, provided by either parent, are positively related to emotional adjustment development. We discuss this in REFER TO PARAGRAPH. It appears that the Reviewer interpreted the word *uniquely* to mean that *only* fathers contribute to emotional adjustment. We intended to say that fathers contribute in a *different* way from mothers.   
We merely intended to summarize fatherhood theory regarding the distinction between the attachment vs activation relationship: An often-cited theory that implies that demandingness is a more important socialization mechanism for fathers than for mothers, and that warmth is a more important socialization mechanism for mothers than for fathers.

@@

<!--[RK14]Socialization; children model their parents and see that their parents are also not able to regulate their emotions??-->

@@

<!-- [RK15]The worse children fare, the more parents want to correct them/put them in line? -->
\WorkInProgress

@@

<!-- WRONG ANSWER!! [RK17]Let op: dit is niet het goede antwoord op de vraag!!! -->

<!--We appreciate this suggestion! Strictly speaking, since Bayesian analyses focus on estimation rather than inference, it is correct to say that the (maximum a-posteriori) estimate is different between mothers and fathers, without further substantiation - because in the Bayesian framework, the maximum a-posteriori estimate can be interpreted as the most likely population value for the parameter, conditional on the data and prior. In practice, since we use Bayesian estimation for pragmatic reasons, we understand that there is added value in knowing the posterior distribution of the difference between mothers and fathers.

Therefore, to address this comment, we have re-run all analyses to obtain the posterior for the differences between mothers and fathers. We have reported this information in-text whenever making a statement about mother/father differences, and have added it to the relevant Supplementary Tables with the full model parameters. We have omitted it from the smaller Tables in the manuscript, because their function is to help make it easier for readers to digest the results, and we feel that adding four columns with difference tests would interfere with that goal. -->

@@

We appreciate the Reviewer's suggestion, and agree that there are probably good grounds to question the linearity of *all* processes within the family system. However, it is not within the scope of the present paper to make that point. In principle, we would be happy to conduct the exploratory analysis proposed by the Reviewer, but we are stopped by the limitations of contemporary statistical software. Including a quadratic term for this non-linear effect requires estimating a latent variable interaction of quantitative involvement with itself. Such latent variable interactions cannot currently be estimated within the Bayesian framework; they require Monte Carlo integration. Thus, we must choose: We can either test our theoretical model, which requires Bayesian estimation using Gibbs sampling, or we analyze this proposed non-linear effect, but within a much simpler model that can be estimated using numerical integration. Our choice to analyze our theoretical model also means deciding *against* testing alternative possible models, such as the one proposed by the Reviewer.

@@

We agree with the Reviewer that mean differences in emotional adjustment based on low vs high involvement are important. That is why we do investigate these effects, and they are reported in the section titled **Effects of quantitative involvement on parenting _and adjustment_**. That is why we suggested those explanations in the Discussion. Here are the relevant fragments from the Results section:
